Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
Various.

The middle and right graphs show results for graph algorithms on the
other two GPUs.  \ADComment{Added this; is it right?}  These
algorithms use barriers, and we experimented with the regular and
query barrier implementations described in \mysec\ref{ }.  The
results shown are for executions that use the more efficient query barrier, except that we also show the gather time associated with the regular barrier for comparison.  The graphs show a similar trend to the left-most graph: as the number of non-cooperative workgroups grows, the
execution time decreases and the gather time increases.\footnote{The right
figure has only 3 points per line: recall that for bfs there are no runs
with ``all-but-one'' non-cooperative workgroups.}
%
The gather time is higher on the right figure: the rmat22 input graph is
rather wide than deep, so the graph algorithm reaches resizing barriers
less often than for the ecology input of the middle figure for
instance. The scheduler thus has fewer opportunities to collect
workgroups and gather time increases. Nonetheless, scheduling
responsiveness can benefit from the query barrier: when used, this
barrier lets the scheduler collect all needed workgroups as soon as they
hit a resizing barrier. As we can see on both the middle and right
figure, the gather time of the query barrier is almost stable w.r.t.\ the
number of workgroups that needs to be collected.

@@

\subsection{Responsiveness graphs}

@@

\subsection{Performance graphs}

>>>>

The middle and right graphs show results for graph algorithms on the
other two GPUs.  \ADComment{Added this; is it right?}  These
algorithms use barriers, and we experimented with the regular and
query barrier implementations described in \mysec\ref{sec:resizingbarrier}.  The
results shown are for executions that use the more efficient query barrier, except that we also show the gather time associated with the regular barrier for comparison.  The graphs show a similar trend to the left-most graph: as the number of non-cooperative workgroups grows, the
execution time decreases and the gather time increases.\footnote{The right
figure has only 3 points per line: recall that for bfs there are no runs
with ``all-but-one'' non-cooperative workgroups.}
%
The gather time is higher on the right figure: the rmat22 input graph is
rather wide than deep, so the graph algorithm reaches resizing barriers
less often than for the ecology input of the middle figure for
instance. The scheduler thus has fewer opportunities to collect
workgroups and gather time increases. Nonetheless, scheduling
responsiveness can benefit from the query barrier: when used, this
barrier lets the scheduler collect all needed workgroups as soon as they
hit a resizing barrier. As we can see on both the middle and right
figure, the gather time of the query barrier is almost stable w.r.t.\ the
number of workgroups that needs to be collected.

@@

\subsection{Responsiveness graphs}\label{appendix:extraresponsiveness}

@@

\subsection{Performance graphs}\label{appendix:extraperformance}
